The low-frequency Murchison radio environment:\\interference analysis and mitigation

### 2014-09-28 articles/2014/MWA-Radio-Environment/mwa-radio-environment.tex
Updating data in log-n log-s plots and some other minor changes

\noindent\begin{figure}
% obs data: 1061583576, 2013-08-26.
\begin{center}\hspace*{-0.2cm}\includegraphics[width=9.1cm]{img/dvb_example}
\caption{RFI from Digital Video Broadcasting (DVB). Because of its broadband nature, this kind of RFI is not well flagged in the initial AOFlagger step. It is detected by a later step by checking the global statistics. This type of RFI makes most of the 30.72~MHz bandwidth unusable. It is not seen very often (1 out of 6 observed nights). }
\label{fig:dvb_example}
\end{center}
\end{figure}

>>>>

\noindent\begin{figure}
% obs data: 1061583576, 2013-08-26.
\begin{center}\hspace*{-0.2cm}\includegraphics[width=9.1cm]{img/dvb_example}
\caption{RFI from Digital Video Broadcasting (DVB). Because of its broadband nature, this kind of RFI is not well flagged in the initial AOFlagger step, but is detectable in the global statistics. This type of RFI makes most of the 30.72~MHz bandwidth unusable. It is visible for about 2 h in 1 out of the 6 nights that observed this band. }
\label{fig:dvb_example}
\end{center}
\end{figure}
